\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-15 main.Rmd
updates intro

The purpose of the calendar-based visualization is to provide insights into people's daily schedules relative to events such as work days, weekends, holidays, and special events. This work was originally motivated by studying foot traffic in the city of Melbourne, Australia [@ped]. There have been 43 sensors installed that count pedestrians every hour across the downtown area (Figure \ref{fig:ped-map}). The dataset can shed light on people's daily rhythms, and assist the city administration and local businesses with event planning and operational management. A routine examination of the data would involve constructing conventional time series plots to catch a glimpse of temporal patterns. The faceted plots in Figure \ref{fig:time-series-plot}, give an overall picture of the foot traffic at 3 different sensors over 2016. Further faceting by day of the week (Figure \ref{fig:facet-time}) provides a better glimpse of the daily and sub-daily pedestrian patterns. The sensor data, like many temporal datasets on human behaviors, lends itself to a number of exploratory data visualization challenges:

1. Variations exist on multiple time scales including time of day, day of week, and day of year (such as public holiday and recurring events).
2. Since the data are often collected at sub-daily frequencies, they typically involve a large number of observations.
3. Measurements of a single type are made at multiple locations at a given time point, which creates the need for comparing and contrasting between locations.

The conventional ways to display time series and constructing faceted displays are insufficient to address these challenges.

@@

The remainder of the paper is organized as follows. Section \ref{sec:algorithm} demonstrates the construction of the calendar layout in depth. Section \ref{sec:opt} lists and describes the options that come with the `frame_calendar` function. Section \ref{sec:variations} presents some variations of its usage. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

@@

The case study uses individual-level energy usage from Australia. The dataset contains half-hourly electricity consumption data of 4 households over different time periods, with `r format(NROW(elec), big.mark = ",")` observations and `r NCOL(elec)` variables. The goal is to sketch typical profiles as well as unusual patterns in order to better understand each household's daily schedules.

Firstly, a letter value plot (ref??) shown as Figure \ref{fig:dow} helps grasp an overview of the variability between households across days of week. Household 2 has seen a great deal of variability in daily energy consumption, depicting relatively large variations on Thursdays. By contrast, household 4 consumes much less energy with constant variations. The dark blue line (representing median) highlights more energy consumed by households 1, 2, and 4 over the weekends relative to weekdays.

>>>>

The purpose of the calendar-based visualization is to provide insights into people's daily schedules relative to events such as work days, weekends, holidays, and special events. This work was originally motivated by studying foot traffic in the city of Melbourne, Australia [@ped]. There have been 43 sensors installed that count pedestrians every hour across the downtown area (Figure \ref{fig:ped-map}). The dataset can shed light on people's daily rhythms, and assist the city administration and local businesses with event planning and operational management. A routine examination of the data would involve constructing conventional time series plots to catch a glimpse of temporal patterns. The faceted plots in Figure \ref{fig:time-series-plot}, give an overall picture of the foot traffic at 3 different sensors over 2016. Further faceting by day of the week (Figure \ref{fig:facet-time}) provides a better glimpse of the daily and sub-daily pedestrian patterns.

<!--
1. Variations exist on multiple time scales including time of day, day of week, and day of year (such as public holiday and recurring events).
2. Since the data are often collected at sub-daily frequencies, they typically involve a large number of observations.
3. Measurements of a single type are made at multiple locations at a given time point, which creates the need for comparing and contrasting between locations.
-->

However, the conventional displays of time series data obscure patterns relative to special events (such as public holidays and recurring cultural/sport events), which may appear more fascinating to viewers.

@@

The remainder of the paper is organized as follows. Section \ref{sec:algorithm} demonstrates the construction of the calendar layout in depth. Section \ref{sec:opt} lists and describes the options that come with the `frame_calendar` function. Section \ref{sec:variations} presents some variations of its usage. Graphical analyses of sub-daily people's activities are illustrated with a case study in Section \ref{sec:case}. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

@@

The case study uses individual-level energy usage from Australia. The dataset contains half-hourly electricity consumption data of 4 households over different time periods, with `r format(NROW(elec), big.mark = ",")` observations. The goal is to sketch typical profiles as well as unusual patterns in order to better understand each household's daily schedules.

Firstly, a letter value plot [@hofmann2017letter] shown as Figure \ref{fig:dow} helps grasp an overview of the variability between households across days of week. Household 2 has seen a great deal of variability in daily energy consumption, depicting relatively large variations on Thursdays. By contrast, household 4 consumes much less energy with constant variations. The dark blue line (representing median) highlights more energy consumed by households 1, 2, and 4 over the weekends relative to weekdays.

### 2018-10-15 main.tex
updates intro

The purpose of the calendar-based visualization is to provide insights
into people's daily schedules relative to events such as work days,
weekends, holidays, and special events. This work was originally
motivated by studying foot traffic in the city of Melbourne, Australia
\citep{ped}. There have been 43 sensors installed that count pedestrians
every hour across the downtown area (Figure \ref{fig:ped-map}). The
dataset can shed light on people's daily rhythms, and assist the city
administration and local businesses with event planning and operational
management. A routine examination of the data would involve constructing
conventional time series plots to catch a glimpse of temporal patterns.
The faceted plots in Figure \ref{fig:time-series-plot}, give an overall
picture of the foot traffic at 3 different sensors over 2016. Further
faceting by day of the week (Figure \ref{fig:facet-time}) provides a
better glimpse of the daily and sub-daily pedestrian patterns. The
sensor data, like many temporal datasets on human behaviors, lends
itself to a number of exploratory data visualization challenges:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Variations exist on multiple time scales including time of day, day of
  week, and day of year (such as public holiday and recurring events).
\item
  Since the data are often collected at sub-daily frequencies, they
  typically involve a large number of observations.
\item
  Measurements of a single type are made at multiple locations at a
  given time point, which creates the need for comparing and contrasting
  between locations.
\end{enumerate}

The conventional ways to display time series and constructing faceted
displays are insufficient to address these challenges.

@@

The remainder of the paper is organized as follows. Section
\ref{sec:algorithm} demonstrates the construction of the calendar layout
in depth. Section \ref{sec:opt} lists and describes the options that
come with the \texttt{frame\_calendar} function. Section
\ref{sec:variations} presents some variations of its usage. Section
\ref{sec:discussion} discusses the advantages and disadvantages of the
method.

@@

The case study uses individual-level energy usage from Australia. The
dataset contains half-hourly electricity consumption data of 4
households over different time periods, with 64,128 observations and 5
variables. The goal is to sketch typical profiles as well as unusual
patterns in order to better understand each household's daily schedules.

Firstly, a letter value plot (ref??) shown as Figure \ref{fig:dow} helps
grasp an overview of the variability between households across days of
week. Household 2 has seen a great deal of variability in daily energy
consumption, depicting relatively large variations on Thursdays. By
contrast, household 4 consumes much less energy with constant
variations. The dark blue line (representing median) highlights more
energy consumed by households 1, 2, and 4 over the weekends relative to
weekdays.

>>>>

The purpose of the calendar-based visualization is to provide insights
into people's daily schedules relative to events such as work days,
weekends, holidays, and special events. This work was originally
motivated by studying foot traffic in the city of Melbourne, Australia
\citep{ped}. There have been 43 sensors installed that count pedestrians
every hour across the downtown area (Figure \ref{fig:ped-map}). The
dataset can shed light on people's daily rhythms, and assist the city
administration and local businesses with event planning and operational
management. A routine examination of the data would involve constructing
conventional time series plots to catch a glimpse of temporal patterns.
The faceted plots in Figure \ref{fig:time-series-plot}, give an overall
picture of the foot traffic at 3 different sensors over 2016. Further
faceting by day of the week (Figure \ref{fig:facet-time}) provides a
better glimpse of the daily and sub-daily pedestrian patterns.

However, the conventional displays of time series data obscure patterns
relative to special events (such as public holidays and recurring
cultural/sport events), which may appear more fascinating to viewers.

@@

The remainder of the paper is organized as follows. Section
\ref{sec:algorithm} demonstrates the construction of the calendar layout
in depth. Section \ref{sec:opt} lists and describes the options that
come with the \texttt{frame\_calendar} function. Section
\ref{sec:variations} presents some variations of its usage. Graphical
analyses of sub-daily people's activities are illustrated with a case
study in Section \ref{sec:case}. Section \ref{sec:discussion} discusses
the advantages and disadvantages of the method.

@@

The case study uses individual-level energy usage from Australia. The
dataset contains half-hourly electricity consumption data of 4
households over different time periods, with 64,128 observations. The
goal is to sketch typical profiles as well as unusual patterns in order
to better understand each household's daily schedules.

Firstly, a letter value plot \citep{hofmann2017letter} shown as Figure
\ref{fig:dow} helps grasp an overview of the variability between
households across days of week. Household 2 has seen a great deal of
variability in daily energy consumption, depicting relatively large
variations on Thursdays. By contrast, household 4 consumes much less
energy with constant variations. The dark blue line (representing
median) highlights more energy consumed by households 1, 2, and 4 over
the weekends relative to weekdays.
